MS Technical Paper: \\ Placement Algorithms for Heterogeneous FPGAs

### 2025-04-18 latex/paper/paper.tex
primitive BEL explanations

    To manage this complexity, Xilinx organizes these BELs into incrementally abstract structures. 
    First, \textbf{BELs} are grouped into \textbf{Sites}. 
    Each Site is embedded into a \textbf{Tile}, and Tiles are further arranged into \textbf{Clock Regions}. 
    In some high-density devices, multiple Clock Regions may be consolidated into one or more \textbf{Super Logic Regions}~(SLRs). 
    However, for the scope of this paper, we focus on Xilinx 7-Series devices with a single SLR.

    In the 7-Series architecture, the term \emph{CLB} (Configurable Logic Block) refers to a \emph{CLB Tile} that contains two \emph{SLICE} Sites. 
    Each SLICE Site has a set of BELs including eight LUTs, eight FFs, and one \emph{CARRY4} adder. 
    These SLICEs provide the core logic and arithmetic functionality of the device.

@@

    \textbf{LUTs} \quad

    \textbf{FFs} \quad

>>>>

    To manage this complexity, Xilinx organizes these BELs into incrementally abstract structures. 
    First, \textbf{BELs} are grouped into \textbf{Sites}. 
    Each Site is embedded into a \textbf{Tile}, and Tiles are further arranged into \textbf{Clock Regions}. 
    In some high-density devices, multiple Clock Regions may be consolidated into one or more \textbf{Super Logic Regions}~(SLRs). 
    However, for the scope of this paper, we focus on Xilinx 7-Series devices with only a single SLR.

    In the 7-Series architecture, the term \emph{CLB} (Configurable Logic Block) refers to a \emph{CLB Tile} that contains two \emph{SLICE} Sites. 
    Each SLICE Site has a set of BELs including eight LUTs, eight FFs, and one \emph{CARRY4} adder. 
    The BELs in these SLICEs facilitate the bulk of the general programmability of the FPGA fabric. 
    We will explain in detail the motivation and function of these BELs.

    \textbf{LUTs} \quad
        Combinational logic is universal to all HDL designs. 
        As the their name suggests, Look‑Up Tables (LUTs) facilitate combinational logic by acting as tiny asynchronously‑accessed ROMs whose contents are fixed when the FPGA is programmed.  
        For any boolean function, the synthesizer precalculates the output to every possible input combination and stores the resulting truth table into a LUT's static memory. 
        The inputs are then essentially treated as an address space that maps to a data value space in an asynchronous ROM. 
        No explicit logic gates like NAND or XNOR are synthesized, contrary to what newcomers might expect from a "Field Programmable Gate Array". 
        In the 7‑Series devices, one LUT can facilitate any 6-input boolean function, or two 5-input functions, as long as they share the same input signals.  
        The LUT can also host two independent boolean functions of up to 3 inputs each, even when the inputs are not shared.  
        Functions requiring more than six unique inputs are decomposed across multiple cascaded LUTs.
        Figure \ref{fig:lut_synthesis} shows an example of where a LUT is typically synthesized in a design entry.

        \begin{figure}[]
            \centering
            \includegraphics[width=9.0cm]{figures/lut_synthesis.png}
            \caption{LUT synthesis from user design}
            \label{fig:lut_synthesis}
        \end{figure}

    \textbf{FFs} \quad
        FFs are synthesized to facilitate synchronous event-driven signal assignment. 
        For most FPGA users, in Verilog, this essentially means assignments wrapped in \texttt{always @(posedge clk)} statements. 
        Figure \ref{fig:ff_synthesis} shows an example of where a flip flop (FF) is typically synthesized. 
        The cell primitive FDRE is a type of FF and belongs to a family of D Flip Flops (DFFs) with Clock Enable (CE). 
        \begin{itemize}
            \item \textbf{FDCE:} DFF with CE and Asynchronous Clear
            \item \textbf{FDPE:} DFF with CE and Asynchronous Preset
            \item \textbf{FDSE:} DFF with CE and Synchronous Set
            \item \textbf{FDRE:} DFF with CE and Synchronous Reset
        \end{itemize}
        In a typical HDL design, the vast majority of FFs will be synthesized as FDREs. 
        A FF BEL may also be used to implement latches, however, since latches are generally known to be bad practice in FPGA design, we will not consider latch synthesis for this paper. 
        \begin{figure}[]
            \centering
            \includegraphics[width=9.0cm]{figures/ff_synthesis.png}
            \caption{FF synthesis from user design}
            \label{fig:ff_synthesis}
        \end{figure}

@@
